`lancer` Output Examples

### 2023-01-27 README.qmd
Try out nre version of lancer.

Type the following command to install R packages `lancer` version 0.1.0.

```{r}
#| eval: false
#| warning: false
#| message: false
devtools::install_github("SLINGhub/lancer", ref = "0.1.0")
```

>>>>

Install these R packages to ensure rendering of Quarto documents is possible.

install.packages("rmarkdown", dependencies = TRUE)
install.packages("markdown", dependencies = TRUE)
```

Type the following command to install R packages `lancer` version 0.1.1.

```{r}
#| eval: false
#| warning: false
#| message: false
devtools::install_github("SLINGhub/lancer", ref = "0.1.1")
```
